---
title: "armdeck"
output: xaringan::moon_reader 
---

class: center, middle

# Introduce yourself!
> My name is Alison and I am a Data Scientist & Professional Educator at RStudio. I live in Portland, Oregon with my husband, daughter, and our sourdough starter.
.left[and babies]
---

class: left, middle

# Find me at...
With images, one can do the html embed.  It's html slides.

![Image of Momtocat](http://bit.ly/momtocat)
---
# Hi there
My name is Kurt

--

I like hot toddies

--

`#rdogladies`

--
and babies

---
.pull-left[
...
<img src="http://bit.ly/wiki-toddy" width="100%" align="right" />
]
.pull-right[
...
<img src="http://bit.ly/wiki-toddy" width="100%" align="right" />
]

---
.pull-left[
```{r plot-last, fig.show = 'hide'}
library(babynames)
library(tidyverse)
tx_names <- babynames %>%
  filter(name == "Dallas" | name == "Austin") %>% 
  filter(sex == "F")
tx_plot <- ggplot(tx_names, 
                    aes(x = year, 
                        y = prop,  
                        group = name, 
                        color = name)) + 
  geom_line() 
tx_plot
```
]
.pull-right[
```{r ref.label = 'plot-last', echo = FALSE}
```
]

---
```{r dev = 'svg', dev.args = list(bg = "transparent")}
name_plot <- ggplot(tx_names , 
                    aes(x = year, 
                        y = prop,  
                        group = name, 
                        color = name)) + 
  geom_line()
invthm <- theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "transparent", colour = NA), 
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.key = element_rect(fill = "transparent", colour = NA),
    text = element_text(colour = "white"),
    axis.text = element_text(colour = "white")
  )
```

---
```{r dev = 'svg', dev.args = list(bg = "transparent")}
name_plot + invthm
```
